---
title: "RWorksheet#7a"
author: "Jeodalyn Edulag BSIT 2-A"
date: "2022-12-13"
output: word_document
---


\hfill\break
1. Create a data frame for the table below 
```{r, include=TRUE}
Student <- seq(1:10)
Pre_Test <- c(55,54,47,57,51,61,57,54,63,58)
Post_Test <- c(61,60,56,63,56,63,59,56,62,61)

j <- data.frame(Student,Pre_Test,Post_Test)
j
```

a. Compute the descriptive statistics using different packages (Hmisc and pastecs). Write the codes and its result.

```{r, include=TRUE}

library(Hmisc)
library(pastecs)

describe(j)

stat.desc(j)
```

\hfill\break
2. The Department of Agriculture was studying the effects of several levels of a
fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
The data were 10,10,10, 20,20,50,10,20,10,50,20,50,20,10.

```{r, include=TRUE}
Fertilizer_Lev <- c(10,10,10,20,20,50,10,
                       20,10,50,20,50,20,10)
```

a. Write the codes and describe the result.
```{r, include=TRUE}
ordr <- factor(Fertilizer_Lev, ordered = TRUE)
ordr
```

\hfill\break
3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study
the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” ,
“l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense
```{r, include=TRUE}
subjs <- c("l","n","n","i","l","l","n","n","i","l")
```

a. What is the best way to represent this in R?
```{r, include=TRUE}
#Dataframe
Df <- data.frame(subjs)
Df
```

\hfill\break
4.Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
```{r, include=TRUE}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
state  
```

a. Apply the factor function and factor level. Describe the results.
```{r, include=TRUE}
jsan <- factor(state)
jsan

levels(jsan)
```

\hfill\break
5. From #4 - continuation:
Suppose we have the incomes of the same tax accountants in another vector (in
suitably large units of money)
```{r, include=TRUE}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```

a. Calculate the sample mean income for each state we can now use the special
function tapply():

```{r, include=TRUE}
m_income <- tapply(incomes,state, mean )
m_income
```

b. Copy the results and interpret.
```{r, include=TRUE}
#     act      nsw       nt 
#44.50000 57.33333 55.50000 
# qld       sa      tas 
#53.60000 55.00000 60.50000 
# vic       wa 
#56.00000 52.25000 
#these are tge mean of income
```

\hfill\break
6.Calculate the standard errors of the state income means (refer again to number 3)
```{r, include=TRUE}
stdError <- function(x) sqrt(var(x)/length(x))
```

a. What is the standard error? Write the codes.
```{r, include=TRUE}
istdr <- tapply(incomes, state, stdError)
istdr
```

b. Interpret the result.
```{r setup, include=TRUE}
#It tells the sample mean of income
```

\hfill\break
7. Use the titanic dataset.
```{r, include=TRUE}

data("Titanic")
titanic<- data.frame(Titanic)
```

a. subset the titatic dataset of those who survived and not survived. Show the
codes and its result.
```{r, include=TRUE}
svives <- subset(titanic, Survived == "Yes")
svives

d <- subset(titanic, Survived == "No")
d  
```

\hfill\break
8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this chronological grouping of the data. You can create this dataset in Microsoft Excel.

a. describe what is the dataset all about.
```{r, include=TRUE}
#The dataset s all about Breast Cancer.
```

b. Import the data from MS Excel. Copy the codes.

```{r, include=TRUE}

library("readxl")
b_cancer <- read_excel("C:\\Desktop\\JEODALYN//Breast_Cancer.xlsx")
b_cancer
```

c. Compute the descriptive statistics using different packages. Find the values of:
c.1 Standard error of the mean for clump thickness.

```{r, include=TRUE}
num8c1.nja <- length(b_cancer$`CL. thickness`)
num8c1.sdja <- sd(b_cancer$`CL. thickness`)
num8c1.sja <- num8c1.sdja/sqrt (b_cancer$`CL. thickness`)
num8c1.sja
```

c.2 Coefficient of variability for Marginal Adhesion.
```{r, include=TRUE}
Marginal_Adh <- as.numeric(b_cancer$V5)
stat.desc(Marginal_Adh)
```

c.3 Number of null values of Bare Nuclei.
```{r, include=TRUE}
B_Nuclei <- as.numeric(b_cancer$V7)
stat.desc( B_Nuclei)
```

c.4 Mean and standard deviation for Bland Chromatin
```{r, include=TRUE}
Bl_Chromatin <- as.numeric(b_cancer$V8)

mean(Bl_Chromatin , na.rm = TRUE) 
sd(Bl_Chromatin , na.rm = TRUE)

stat.desc( Bl_Chromatin)
```

c.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r, include=TRUE}
c_shape <- as.numeric(b_cancer$V4)
stat.desc(c_shape )
```

d. How many attributes?
```{r, include=TRUE}
attributes(b_cancer)
```

e. Find the percentage of respondents who are malignant. 
Interpret the results.
```{r, include=TRUE}
describe(b_cancer$V11, na.rm =TRUE)
```

\hfill\break
9. Export the data abalone to the Microsoft excel file. Copy the codes.
```{r, include=TRUE}
library("AppliedPredictiveModeling")
data("abalone")
head(abalone)
summary(abalone)

library(xlsx)
write.xlsx("abalone", "C:\\Desktop\\Jeodalyn1\\JEODALYN1.xlsx")
```

