---
title: 'RWorksheet #5'
author: "Jeodalyn Edulag BSIT 2-A"
date: "2022-11-22"
output: pdf_document
---
\hfill\break
1. The table shows the enrollment of BS in Computer Science,
SY 2010-2011.

```{r, vector = TRUE}
cas <- data.frame("Course Year" = c ("1st", "2nd", "3rd",
                                     "4th"), " 2019–2020" =
                                      c(80, 75, 70, 60))
cas

```

a. Plot the data using a bar graph. Write the codes and 
copy the result.

```{r, vector = TRUE}

e <- c("1st" = 80, "2nd" = 75, "3rd" = 70, "4th" = 60)
barplot(e)

```

b. Using the same table, label the barchart with 
Title = ” Enrollment of BS Computer Science
horizontal axis = “Curriculum Year” and
vertical axis = “number of students”

```{r, vector = TRUE}

b <- c("1st" = 80 , "2nd" = 75, "3rd" = 70, "4th" = 60)
b
barplot(b, 
        main = "Enrollment of BS Computer Science", 
        xlab = "Number of Students", 
        ylab = "Course Year")

```

\hfill\break
2. The monthly income of De Jesus family was spent on the
following:
60% on Food, 10% on electricity, 5% for savings, and
25% for other miscellaneous expenses 

a. Create a table for the above scenario.
Write the codes and its result.
```{r, vector = TRUE}

bills <- c("Food", "Electricity", "Savings", 
        "Miscellaneous_expenses")
exp <- c(60, 10, 5, 25)

m <- data.frame(bills, exp)
m

l <- table(m)
l

```

b. Plot the data using a pie chart. Add labels, colors and 
legend. Write the codes and its result.

```{r, vector = TRUE}

exp <- c(60, 10, 5, 25)
d <- round(exp/sum(exp)*100,1)
d <- paste(d, "%", sep = " ")

jchart <- pie( exp, labels = d, cex = 0.8, col = rainbow(4), 
               main = "De Jesus family Monthly Expenses")
legend("topright", c("Food", "Electricity", "Savings", 
                      "Miscellaneous"),
                      cex = 0.8 , fill =rainbow(4))

```

\hfill\break
3. Open the mtcars dataset.

a. Create a simple histogram specifically for mpg 
(miles per gallon) variable.Use $ to select the mpg only.
Write the codes and its result.

```{r, vector = TRUE}

data(mtcars)

mt <- (mtcars$mpg)
mt

hist(mt, breaks=12)

```

b. Colored histogram with different number of bins.

```{r, vector = TRUE}

hist(mtcars$mpg, breaks=12, col="red")

```

c. Add a Normal Curve

```{r, vector = TRUE}

x <- mtcars$mpg
h <-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
           main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)

```

\hfill\break
4. Open the iris dataset. Create a subset for each species.
a. Write the codes and its result.

```{r, vector = TRUE}

data("iris")

julz <- data.frame(iris)
julz

df_set <- data.frame(iris)
df_set

df_vir <- data.frame(iris)
df_vir

df_verclr <- data.frame(iris)
df_verclr

s1 <- subset(df_set, Species == 'setosa' )
s1

vs1 <- subset(df_vir, Species == 'versicolor' )
vs1

vir1 <- subset(df_verclr, Species == 'virginica' )
vir1

```

b. Get the mean for every characteristics of each species using colMeans().
Write the codes and its result.

```{r, vector = TRUE}

seto_1 <- colMeans(s1[sapply(df_set,is.numeric)])
seto_1

vir_2 <- colMeans(vir1[sapply(df_vir,is.numeric)])
vir_2

vs2 <- colMeans(vs1[sapply(df_verclr,is.numeric)])
vs2

```

c. Combine all species by using rbind()
The table should be look like this:

```{r, vector = TRUE}

jla <- rbind( seto_1, vs2, vir_2)
bem_df <- data.frame(jla)
bem_df

```

d. From the data in 4-c: Create the barplot().
Write the codes and its result.
The barplot should be like this.

```{r, vector = TRUE}

barplot(height = as.matrix(bem_df),main = "Iris Data",
        ylab = "Mean Scores",
        beside =T, col = rainbow(3))

```
