---
title: "RWorksheet 3b in R"
author: "Jeodalyn Edulag BSIT 2-A"
date: "2022-11-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\hfill\break

#1. Create a data frame using the table below.

#| a. Write the codes.

```{r, vector = TRUE}
rspndts <- c(seq(1:20))
sex <- c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2,
        2, 2, 2, 2, 2, 1, 2)
f_occup <- c(1, 3, 3, 3, 1, 2, 3, 1, 1, 1, 3, 2, 1, 3, 3,
             1, 3, 1, 2, 1)
p_home <- c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8, 3,
            11, 7, 6)
s_sch <- c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1,
           2, 5, 3, 2) 
t_houses <- c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3,
              3, 3, 3, 2)

df <- data.frame(rspndts, sex, f_occup, p_home, s_sch,
                      t_houses)
df

```

#b. Describe the data. Get the structure or the summary of the data

```{r, vector = TRUE}
summary(df)

```

#c. Is the mean number of siblings attending is 5?

```{r, vector = TRUE}
##Answer: No, the mean number of siblings 
##attending school is 2.95

```

#d. Extract the 1st two rows and then all the columns using the subsetting functions. Write the codes and its output.

```{r, vector = TRUE}
ext <- subset(df[1:2, 1:6, drop =FALSE])
ext

```

#e. Extract 3rd and 5th row with 2nd and 4th column.
#Write the codes and its result.

```{r, vector = TRUE}
ext1 <- subset(df[c(3,5), c(2,4)])
ext1

```

#f. Select the variable types of houses then store the vector #that results as types_houses. Write the codes.

```{r, vector = TRUE}
Typesofhouses <- df$t_houses
Typesofhouses

```

#g. Select only all Males respondent that their father 
#occupation was farmer. Write the codes and its output.

```{r, vector = TRUE}
frmr <- subset(df[c(1:20), c(2,3)])
frmr

male <- frmr[df$f_occup == '1',]
male
```

#h. Select only all females respondent that have greater #
#than or equal to 5 number of siblings attending school. 
#Write the codes and its outputs.

```{r, vector = TRUE}
s_fml <- subset(df[c(1:20), c(2,5)])
s_fml

fmale <- s_fml[df$s_sch >= '5',]
fmale

```

\hfill\break

#2. Write a R program to create an empty data frame. 
#Using the following codes:

df <- data.frame (
  Ints = integer(),
  Doubles=double(), 
  Characters = character(),
  Logicals=logical(),
  stringsAsFactors = FALSE
)

print ("Structures of the empty dataframe: ")
print(str(df))

#a. Describe the results. 

```{r, vector = TRUE}
##The data frame has zero columns, 5 rows and zero level.

```

\hfill\break

#3. Interpret the graph.

```{r, vector = TRUE}
T_SentimentTwts <- print ("My interpretation of the graph that shows Donald Trump's daily sentiments in his tweets is that each day, the count of negative sentiments prevails, which indicates that there are significantly more negative sentiments than positive or neutral ones. Positive rankings came next, and they were followed by neutral rankings. To sum up, a large portion of Twitter users dislike Donald Trump as a politician, which explains their unfavorable views of him.")
T_SentimentTwts

```
