---
title: 'RWorksheet #4'
author: "Jeodalyn Edulag"
date: "2022-11-23"
output: pdf_document
---

\hfill\break
1.The table below shows the data about shoe size and height.
Create a data frame.

```{r, vector = TRUE}
s_size <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,
            10.5,8.5,12.0,10.5)
hght <- c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,
          64.0,74.5,67.0,71.0,71.0)
gen <- c("F","F","F","F","M","F","F","F","M","F","M",
         "F","M","M")
S_size <- c(13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,
            8.5,10.5,11.0,9.0,13.0)
Hght <- c(77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,
          69.0,72.0,70.0,69.0,70.0)
Gen <- c("M","M","F","F","M","F","F","M","M","F",
         "M","M","M","M")

dfrm <- data.frame(s_size,hght, gen, S_size, 
                   Hght, Gen)
dfrm

```

a. Describe the data.
```{r, vector = TRUE}
##The data shows the different shoe size among male and female in different heights.

```

b. Find the mean of shoe size and height of the respondents. Copy the codes and results.
```{r, vector = TRUE}
m1 <- mean(s_size)
m1

m2 <- mean(S_size)
m2

ttl <- c(m1, m2)
ttl

# Total shoe size mean.
s_mean <- mean(ttl)
s_mean

m3 <- mean(hght)
m3

m4 <- mean(Hght)
m4

ttl1 <- c(m3, m4)
ttl1

# Total height mean.
h_mean <- mean(ttl1)
h_mean

```

c. Is there a relationship between shoe size and height? Why?
```{r, vector = TRUE}
##Yes, there is a relationship between shoe size and height, 
##the shoe sizes is big when the respondents is also tall.
##If the height of the respondents is below 70.0 their shoe 
##size will be small.

```

#Factors
\hfill\break
2.Construct character vector months to a factor with factor() 
and assign the result to factor_months_vector. Print out 
factor_months_vector and assert that R prints out the 
factor levels below the actual values.Consider data 
consisting of the names of months:
```{r, vector = TRUE}
months_vector <- c("March","April","January","November",
                   "January","September","October","September",
                   "November","August","January","November",
                   "November", "February","May","August",
                   "July","December","August",
                   "August","September","November",
                   "February","April")

factor_months_vector <- factor(months_vector)
factor_months_vector

```

\hfill\break
3. Then check the summary() of the months_vector and 
factor_months_vector. Interpret the results of both vectors.
Are they both equally useful in this case?

```{r, vector = TRUE}
smy <- summary(months_vector)
smy

smy1 <- summary(factor_months_vector)
smy1

##Both of the vector summary are useful because at the 
##summary of months_vector tells us about the length, class, 
##and mode. In summary of factor_months_vector it tells 
##us how many repeating elements there are.

```

\hfill\break
4. Create a vector and factor for the table below.

```{r, vector = TRUE}

Direction <- c("East", "West", "North") 
Frequency <- c(1, 4, 3)
a <- factor(Direction)
b <- factor(Frequency)
print(a)
print(b)

```

5. Enter the data below in Excel with 
file name = import_march.csv

a.Import the excel file into the Environment Pane using
read.table() function. Write the code.
```{r, vector = TRUE}
j <- read.table("/cloud/project/RWorksheet_Edulag#4/import_march.csv", header= TRUE, sep= "," )
j

```

b. View the dataset. Write the code and its result.
```{r, vector = TRUE}
e <- read.csv("/cloud/project/RWorksheet_Edulag#4/import_march.csv")
e

```
